### 2013-04-09 R/reportmd.Rmd
Improved formatting of knitr report

Report for study: `r .study`
========================================================

Study reference: `r .dat$ref`

Study contact: `r .dat$contact$name`.

Contact email: `r .dat$contact$email`.

Contact address: `r .dat$contact$address`.

Data description
-----------------------------------

@@

Number of records for each variable
-----------------------------------

@@

More details
------------------------------------

### Please check if the points on the map match locations and coordinates

@@

### Please analyse if points on country map match locations and coordinates

@@

### Location level - please provide any missing information
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
locLevelInfo(.dat$data)
```

### Stand level - please provide any missing information
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
standLevelInfo(.dat$data)
```

### Species level - please provide any missing information
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
spLevelInfo(.dat$data)
```

### Method - please provide any missing information/follow template
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
printMeta(.dat$data)
```

Plot of data
---------------------------------

>>>>

# Report for study: `r .study`

**Reference:** `r .dat$ref[2]`

**Data contributor:** `r .dat$contact$name`.

**Email:** `r .dat$contact$email`.

**Address:** `r .dat$contact$address`.

## Overview of data provided

@@

### Number of records for each variable

@@

## Study details

### Location

**Location dtaa**
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
locLevelInfo(.dat$data)
```

**Global map**

@@

**Country map**

@@

**Stand description**

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
standLevelInfo(.dat$data)
```

### Species data

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
spLevelInfo(.dat$data)
```

### Methods
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
metaTable  <-  printMeta(.dat$data)
for(j in 1:nrow(metaTable)){
  cat(paste0(metaTable[j,1], ": ", metaTable[j,2], "\n\n"))
}

```

## Plots of data
